Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-21 paper-1/manuscript.tex
Rev Fig6 caption

\begin{figure*}%
    \centering
    \includegraphics{fig6.pdf}
    \caption{}
    \label{fig6}
\end{figure*}
\textbf{Fig. 6} Dev non-target responses are reduced due to adaptation.
\textbf{a} Non-target response contrasts in the sample network: The replacement contrast (top right) compares the response to B in msc (top left) to all non-target responses in msc (top center). The adaptation contrast (bottom right) compares the response to B in dev (bottom left) to the response to B in msc (bottom center). Both contrasts together add up to the non-target contrast (dev - msc) shown in Figure \ref{fig5}b. Note that the contrast column (right) shares a color scale to allow a direct comparison.
\textbf{b} Network-wide mean replacement (left) and adaptation (right) contrasts across networks and stimuli, as well as the mean replacement contrast filtered for neurons near B, i.e., neurons within one excitatory synapse of the neurons under direct stimulation of B (center).
\textbf{c} Mean $V_{TA}$ contrast (dev - msc) at the start of A trials, filtered for neurons near B. Each marker corresponds to one network; the sample network is highlighted in red. The histogram in the background shows the distribution of the data, with the orange portion indicating the 95\% confidence interval of the median, calculated by bootstrap with 10000 iterations

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig6.pdf}
    \caption{}
    \label{fig6}
\end{figure*}
\textbf{Fig. 6} Dev non-target responses are reduced due to adaptation, which is caused by greater activity in the early responders to B.
\textbf{a} Non-target response contrasts in the sample network: The replacement contrast (top right) compares the response to B in msc (top left) to all non-target responses, including B, in msc (top center). The adaptation contrast (bottom right) compares the response to B in dev (bottom left) to the response to B in msc (bottom center). Both contrasts together add up to the non-target contrast (dev - msc) shown in Figure \ref{fig5}b. Note that the contrast column (right) shares a color scale to allow direct comparison.
\textbf{b} Network-wide mean replacement and adaptation contrasts across networks and stimuli.
\textbf{c} Relationship across networks and stimuli between the replacement contrast and the contrast in $V_{TA}$ at the start of A trials, and associated linear regression. For both measures, only the first 100 neurons to respond to stimulation by B in any condition were included. Each marker corresponds to one network and target stimulus.
